A parametric system for generating contour parallel toolpaths with adaptive extrusion width

### 2019-08-23 4_method.tex
'skeleton'/'graph' => 'ST'

\subsection{Center classification}\label{sec_center_classification}
The naive method of performing constant width offset produces large overfill and underfill areas on central regions of the skeleton.
These central regions present themselves as upper ridges in the mountains of the UoC surface.
This sections covers what parts of the UoC will be marked as being central, rather than peripheral.

We mark a node of the skeleton as central if its feature radius is larger than that of all of the neighboring nodes in the skeletal graph.
That is: we mark the local maxima, i.e. the mountain tops of the UoC as being central.
We also mark whole bones as being central if they are significant according to a significance measure which is commonly used in shape analysis.

\subsubsection{Significance measure}\label{sec:significance_measure}
Centrality can be formalized by looking at a commonly used significance measure knows as the \emph{bisector angle}.
The bisector angle $\alpha$ is the interior angle $\angle{p_ovp_1} \leq \si{180}{\degree}$ between a location $v$ on a bone of the skeleton and its two supporting polygon points $p_0$ and $p_1$.\cite{attali1996modeling}
Bones are significant if the bisector angle exceeds $\alpha_\text{max}$ which is governed by the beading strategy.

For a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$, which corresponds to overfill areas and underfill areas the size of $\nicefrac12 w^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$ when filled using a naive strategy of constant bead width $w$.
See \cref{naive_overfill_underfill}.
The bisector angle is therefore an exact measure of the amount of overfill and underfill in the naive toolpaths of constant width.
%Contrary to related literature we will \emph{keep} the non-significant regions of the skeleton.
We mark all significant bones as such and contrary to related literature we keep the unmarked bones of the skeleton.
Our framework will decide on a beading at all of the marked nodes in `the center' nodes and apply the beading outward to the unmarked nodes.

@@

A computationally efficient way to compute whether an edge is significant can be obtained by looking at the ratio between feature radius $R$ and the Euclidean distance:
if $ | R(v_1) - R(v_0) | / |v_1 - v_0| >  \cos(\alpha_\text{max} / 2)$ then $\alpha > \alpha_\text{max}$.
See \cref{distance_based_angles}.
This means we can prevent executing trigonometric functions on \emph{each} of the bones in the skeleton.
Moreover the ratio has a clear geometrical interpretation as the slope of the ridge in the UoC surface.

This ratio can readily be applied to simple skeleton segments to determine whether they are significant.
For skeletal segments generated by a polygon vertex at $(0,d)$ and a line segment through $(0,0)$ and $(0,\epsilon)$ or another vertex $(0,0)$, we can determine the significant portion by evaluating $\frac{\partial R}{\partial x} > \cos(\alpha_\text{max} / 2)$.
For parabolas we introduce extra points in the discretization at the two bounds where $| x | = d  / \tan(\alpha_\text{max} / 2)$
and for bones with vertex-vertex support we introduce discretization points at the two bounds where $| x | = \nicefrac12 d  / \tan(\alpha_\text{max} / 2)$.
This ensures that the discretization doesn't alter the extent and existence of marked central regions.
See \cref{legend}.

\begin{figure} \centering
\newlength{\significancePropertiesHeight}
\setlength{\significancePropertiesHeight}{.25\columnwidth}
\begin{subfigure}{0.35\columnwidth} \centering
\includegraphics[height=\significancePropertiesHeight]{sources/method/distance_based_angles.pdf}
\caption{Significance}
\label{distance_based_angles}
\end{subfigure}
\begin{subfigure}{0.3\columnwidth} \centering
\includegraphics[height=\significancePropertiesHeight]{sources/method/distance_ratio_limit.pdf}
\caption{Distance}
\label{distance_ratio_limit}
\end{subfigure}
\begin{subfigure}{0.3\columnwidth} \centering
\includegraphics[height=\significancePropertiesHeight]{sources/method/branch_upward_edge_property.pdf}
\caption{Upward edge}
\label{branch_upward_edge_property}
\end{subfigure}
\caption{
Properties of feature radius $R$.
Part of outline shape in thick black,
skeleton in red,
inscribed circle in gray,
radii in dashed lines.
\subref{distance_based_angles} The significance measure can be simplified using $\alpha = 2 \gamma = 2 \cos^{-1} \Delta R / |v_1 - v_0|$.
\subref{distance_ratio_limit} The distance $|v_1 - v_0| > \Delta R$ because otherwise the feature radius would not be one of an inscribed circle.
\subref{branch_upward_edge_property} The radial distance can only increase along one edge around a branch point in the medial axis.
}
\end{figure}

@@

\subsubsection{Properties of significant regions}
%\begin{lemma} \label{min_euclidean_distance} >> this paragraph contains two lemmas and a concluding remark!
The Euclidean distance between two skeletal vertices can never be less than the difference in the feature radius $R$ measure between the vertices.
See \cref{distance_ratio_limit}.
The condition $|v - p| = \Delta R$ is true exactly for those sekeletal bones between a node $v$ and an outline location $p$ added by the trapezoidation, which means that the trapezoidation never introduces marked bones, so we can perform the trapezoidation after marking.

\iffalse
% This fact is not used anymore, because we change the marking such that it doesn't hold for marked edges any more.
A node in the graph can have at most two significant edges.
For a node in the VD $v$ with a support of three points on the outline polygon $p_1, p_2, p_3$, the bisector angles $\angle{p_1vp_2} + \angle{p_2vp_3} + \angle{p_3vp_1} = 360\degree$, so if two angles are more than $\alpha_\text{max} > 120\degree$ the third one needs to be smaller than $360\degree - 2\alpha_\text{max} < 120\degree$ and therefore nonsignificant.
% However, because of some filtering operations this property does not neccesarily hold for the markings.
The extra edges added to the VD to form the ST can never be significant because their bisector angle is \SI{0}{\degree} by definition,
so the nodes of the ST also have at most two significant edges.
\fi

\begin{lemma}\label{saddle_points_are_marked}
A saddle point is always marked, i.e.\
when traversing the skeletal graph from one locally maximal $R$ to another we must pass through a significant region.
\end{lemma}
\begin{proof}
You will either go through the marked region of a discretized parabola or of a segment with two polygonal vertices as support.
This means that the feature radius function in between marked regions is always monotonic.
This means that when propagating beadings downward from marked regions they can never conflict in the middle - they will always conflict at either marked region.
\end{proof}

\begin{lemma}\label{single_upward_edge}
From any node in the graph which is not a saddle point there is at most a single edge going upward.
\end{lemma}
\begin{proof}
Any branch point $v$ in the MAT coincides with the circumcircle of its support $p_0, p_1, p_2$.
If $v$ lies within $\triangle p_0 p_1 p_2$ it is a local maximum and otherwise we will show it has exactly one upward edge.
If $v$ lies outside of $\triangle p_0 p_1 p_2$ then those support points lie within a \SI{180}{\degree} range from $v$
and one point lies in the middle, say $\angle p_0 + \angle p_1 = \angle p_2$.
Then a circle with radius $R(v) + \epsilon$ around $v'$ such that $|v-v'| < \epsilon$ can only touch $p_0$ and $p_2$.
See \cref{branch_upward_edge_property}.
%See VoronoiQuadrangulation::filterUnmarkedRegions
Bones added because of the trapezoidation always go down to $R=0$, so these don't change the property that each node has at most a single upward edge.
This means that walking up the graph from a marked region to a local maximum follows a single path without branching.
\end{proof}

@@

We first assign each marked node $v$ of the skeleton the bead count $b^*_v \leftarrow f(2R(v))$.
We then filter out short unmarked regions where the bead count remains constant in order to limit the extent of a problem handled in \cref{section_beading_conflicts}.
From each marked node $v_0$ with an upward unmarked bone attached we walk along the upward edges until we hit another marked node $v_1$.
If the upper node has the same bead count $b^*_{v_1} = b^*_{v_0}$ we mark all bones and nodes $v$ in between, and set the bead count $b^*_v \leftarrow b^*_{v_0}$.

\begin{figure*}
\centering
\setlength{\figwidth}{0.13\textwidth}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__bead_count.pdf}
\caption{Flattened bead counts}\label{beading_transitioning_filtering__bead_count}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transition_mids.pdf}
\caption{Transition anchors}\label{beading_transitioning_filtering__transition_mids}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__filtered.pdf}
\caption{Filtered anchors}\label{beading_transitioning_filtering__filtered}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transition_ends.pdf}
\caption{Transition ramp ends}\label{beading_transitioning_filtering__transition_ends}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transitions_applied.pdf}
\caption{Radial support bones}\label{beading_transitioning_filtering__transitions_applied}
\end{subfigure}
\begin{subfigure}{.27\textwidth}
\hspace*{-.5cm}\includegraphics[width=1.2\columnwidth]{sources/method/beading_transitioning_filtering__result_uoc.png}
\caption{Result UoC}\label{beading_transitioning_filtering__result_uoc}
\end{subfigure}
\caption{
Applying bead counts and transitioning on a shape showing the difference between a simple skeleton (top) and a mirrored version with small perturbations in the outline (bottom).
Outline in black, medial axis edges in red, radial edges in grey.
\subref{beading_transitioning_filtering__bead_count} First we initialize the bead counts (black) in the marked regions (blue).
\subref{beading_transitioning_filtering__transition_mids} We then extract the anchor locations (purple) of the transitions to a different bead count should be.
\subref{beading_transitioning_filtering__filtered} We then filter out regions of constant bead count.
\subref{beading_transitioning_filtering__transition_ends} We then calculate the end locations (magenta, pink) of the transitions and modify the bead count at nodes in between to fractional values.
\subref{beading_transitioning_filtering__transitions_applied} Finally we introduce nodes at the ends and introduce radial edges (purple) as per the trapezoidation constraint.
The symmetry in the result shows that transitioning is robust against small perturbations in the outline shape.
}
\label{beading_transitioning_filtering}
\end{figure*}

@@

A transition with length $t(n)$ will be placed somewhere covering the transition anchor position.
We require an additional function to be specified by the beading strategy: $t_0(n)$ determines the distance between the lower end of a transition from bead count $n$ to $n+1$ and the anchor point - as measured along the marked bones of the skeleton.
From that we calculate $t_1(n) = t(n) - t_0(n)$ for the distance from the anchor to the upper end of the transition.
For our example we can simply use $t_0(n) = t_1(n) = \nicefrac12 w_\text{pref}$, so that the transition ramp is centered on the anchor position.

@@

\subsubsection{Beading interpolation}\label{section_beading_interpolation}
Central nodes which are in the middle of a transition have obtained a fractional bead count, but the definition of a beading presupposed integer numbers.
In order to generate a beading for a central node with a fractional bead count assigned we use the fractional part of the bead count to interpolate between two beadings defined on the fractional bead count rounded up and down.
Suppose we want to interpolate between two beadings $B^V$ and $B^W$, for which $n^{B^V} < n^{B^W}$.
We interpolate the diameter $d$, widths $w_i$ and locations $l_i$ for indices $i < \nicefrac12 n^{B^V}$ linearly and enforce the symmetry constraints on the upper indices.
See \cref{beading_interpolation}.
The linear interpolation enforces robustness against small perturbations in the outline shape which cause extra bones to appear in the skeleton inside of transition regions.

>>>>

\subsection{Center classification}\label{sec_center_classification}
The naive method of performing constant width offset produces large overfill and underfill areas on central regions of the ST.
These central regions present themselves as upper ridges in the mountains of the UoC surface.
This sections covers what parts of the UoC will be marked as being central, as opposed to peripheral.

We mark a node in the ST as central if its feature radius is larger than that of all of the neighboring nodes.
That is: we mark the local maxima, i.e. the mountain tops of the UoC as being central.
We also mark whole bones as being central if they are significant according to a significance measure which is commonly used in shape analysis.

\subsubsection{Significance measure}\label{sec:significance_measure}
Centrality can be formalized by looking at a commonly used significance measure knows as the \emph{bisector angle}.
The bisector angle $\alpha$ is the interior angle $\angle{p_ovp_1} \leq \si{180}{\degree}$ between a location $v$ on a bone of the ST and its two supporting polygon points $p_0$ and $p_1$.\cite{attali1996modeling}
Bones are significant if the bisector angle exceeds $\alpha_\text{max}$ which is governed by the beading strategy.

For a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$, which corresponds to overfill areas and underfill areas the size of $\nicefrac12 w^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$ when filled using a naive strategy of constant bead width $w$.
See \cref{naive_overfill_underfill}.
The bisector angle is therefore an exact measure of the amount of overfill and underfill in the naive toolpaths of constant width.
%Contrary to related literature we will \emph{keep} the non-significant regions of the skeleton.
We mark all significant bones as such and contrary to related literature we keep the unmarked bones of the ST.
Our framework will decide on a beading at all of the marked nodes in `the center' nodes and apply the beading outward to the unmarked nodes.

@@

A computationally efficient way to compute whether an edge is significant can be obtained by looking at the ratio between feature radius $R$ and the Euclidean distance:
if $ | R(v_1) - R(v_0) | / |v_1 - v_0| >  \cos(\alpha_\text{max} / 2)$ then $\alpha > \alpha_\text{max}$.
See \cref{distance_based_angles}.
This means we can prevent executing trigonometric functions on \emph{each} of the bones in the ST.
Moreover the ratio has a clear geometrical interpretation as the slope of the ridge in the UoC surface.

This ratio can readily be applied to simple ST segments to determine whether they are significant.
For segments generated by a polygon vertex at $(0,d)$ and a line segment through $(0,0)$ and $(0,\epsilon)$ or another vertex $(0,0)$, we can determine the significant portion by evaluating $\frac{\partial R}{\partial x} > \cos(\alpha_\text{max} / 2)$.
For parabolas we introduce extra points in the discretization at the two bounds where $| x | = d  / \tan(\alpha_\text{max} / 2)$
and for bones with vertex-vertex support we introduce discretization points at the two bounds where $| x | = \nicefrac12 d  / \tan(\alpha_\text{max} / 2)$.
This ensures that the discretization doesn't alter the extent and existence of marked central regions.
See \cref{legend}.

\begin{figure} \centering
\newlength{\significancePropertiesHeight}
\setlength{\significancePropertiesHeight}{.25\columnwidth}
\begin{subfigure}{0.35\columnwidth} \centering
\includegraphics[height=\significancePropertiesHeight]{sources/method/distance_based_angles.pdf}
\caption{Significance}
\label{distance_based_angles}
\end{subfigure}
\begin{subfigure}{0.3\columnwidth} \centering
\includegraphics[height=\significancePropertiesHeight]{sources/method/distance_ratio_limit.pdf}
\caption{Distance}
\label{distance_ratio_limit}
\end{subfigure}
\begin{subfigure}{0.3\columnwidth} \centering
\includegraphics[height=\significancePropertiesHeight]{sources/method/branch_upward_edge_property.pdf}
\caption{Upward edge}
\label{branch_upward_edge_property}
\end{subfigure}
\caption{
Properties of feature radius $R$.
Part of outline shape in thick black,
ST edges in red,
inscribed circle in gray,
radii in dashed lines.
\subref{distance_based_angles} The significance measure can be simplified using $\alpha = 2 \gamma = 2 \cos^{-1} \Delta R / |v_1 - v_0|$.
\subref{distance_ratio_limit} The distance $|v_1 - v_0| > \Delta R$ because otherwise the feature radius would not be one of an inscribed circle.
\subref{branch_upward_edge_property} The radial distance can only increase along one edge around a branch point in the medial axis.
}
\end{figure}

@@

\subsubsection{Properties of significant regions}
%\begin{lemma} \label{min_euclidean_distance} >> this paragraph contains two lemmas and a concluding remark!
The Euclidean distance between two ST vertices can never be less than the difference in the feature radius $R$ measure between the vertices.
See \cref{distance_ratio_limit}.
The condition $|v - p| = \Delta R$ is true exactly for those sekeletal bones between a node $v$ and an outline location $p$ added by the trapezoidation, which means that the trapezoidation never introduces marked bones, so we can perform the trapezoidation after marking.

\iffalse
% This fact is not used anymore, because we change the marking such that it doesn't hold for marked edges any more.
A node in the ST can have at most two significant edges.
For a node in the VD $v$ with a support of three points on the outline polygon $p_1, p_2, p_3$, the bisector angles $\angle{p_1vp_2} + \angle{p_2vp_3} + \angle{p_3vp_1} = 360\degree$, so if two angles are more than $\alpha_\text{max} > 120\degree$ the third one needs to be smaller than $360\degree - 2\alpha_\text{max} < 120\degree$ and therefore nonsignificant.
% However, because of some filtering operations this property does not neccesarily hold for the markings.
The extra edges added to the VD to form the ST can never be significant because their bisector angle is \SI{0}{\degree} by definition,
so the nodes of the ST also have at most two significant edges.
\fi

\begin{lemma}\label{saddle_points_are_marked}
A saddle point is always marked, i.e.\
when traversing the ST from one locally maximal $R$ to another we must pass through a significant region.
\end{lemma}
\begin{proof}
You will either go through the marked region of a discretized parabola or of a segment with two polygonal vertices as support.
This means that the feature radius function in between marked regions is always monotonic.
This means that when propagating beadings downward from marked regions they can never conflict in the middle - they will always conflict at either marked region.
\end{proof}

\begin{lemma}\label{single_upward_edge}
From any node in the ST which is not a saddle point there is at most a single edge going upward.
\end{lemma}
\begin{proof}
Any branch point $v$ in the MAT coincides with the circumcircle of its support $p_0, p_1, p_2$.
If $v$ lies within $\triangle p_0 p_1 p_2$ it is a local maximum and otherwise we will show it has exactly one upward edge.
If $v$ lies outside of $\triangle p_0 p_1 p_2$ then those support points lie within a \SI{180}{\degree} range from $v$
and one point lies in the middle, say $\angle p_0 + \angle p_1 = \angle p_2$.
Then a circle with radius $R(v) + \epsilon$ around $v'$ such that $|v-v'| < \epsilon$ can only touch $p_0$ and $p_2$.
See \cref{branch_upward_edge_property}.
%See VoronoiQuadrangulation::filterUnmarkedRegions
Bones added because of the trapezoidation always go down to $R=0$, so these don't change the property that each node has at most a single upward edge.
This means that walking up the ST from a marked region to a local maximum follows a single path without branching.
\end{proof}

@@

We first assign each marked node $v$ of the ST the bead count $b^*_v \leftarrow f(2R(v))$.
We then filter out short unmarked regions where the bead count remains constant in order to limit the extent of a problem handled in \cref{section_beading_conflicts}.
From each marked node $v_0$ with an upward unmarked bone attached we walk along the upward edges until we hit another marked node $v_1$.
If the upper node has the same bead count $b^*_{v_1} = b^*_{v_0}$ we mark all bones and nodes $v$ in between, and set the bead count $b^*_v \leftarrow b^*_{v_0}$.

\begin{figure*}
\centering
\setlength{\figwidth}{0.13\textwidth}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__bead_count.pdf}
\caption{Flattened bead counts}\label{beading_transitioning_filtering__bead_count}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transition_mids.pdf}
\caption{Transition anchors}\label{beading_transitioning_filtering__transition_mids}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__filtered.pdf}
\caption{Filtered anchors}\label{beading_transitioning_filtering__filtered}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transition_ends.pdf}
\caption{Transition ramp ends}\label{beading_transitioning_filtering__transition_ends}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transitions_applied.pdf}
\caption{Radial support bones}\label{beading_transitioning_filtering__transitions_applied}
\end{subfigure}
\begin{subfigure}{.27\textwidth}
\hspace*{-.5cm}\includegraphics[width=1.2\columnwidth]{sources/method/beading_transitioning_filtering__result_uoc.png}
\caption{Result UoC}\label{beading_transitioning_filtering__result_uoc}
\end{subfigure}
\caption{
Applying bead counts and transitioning on a shape showing the difference between a simple ST (top) and a mirrored version with small perturbations in the outline (bottom).
Outline in black, medial axis edges in red, radial edges in grey.
\subref{beading_transitioning_filtering__bead_count} First we initialize the bead counts (black) in the marked regions (blue).
\subref{beading_transitioning_filtering__transition_mids} We then extract the anchor locations (purple) of the transitions to a different bead count should be.
\subref{beading_transitioning_filtering__filtered} We then filter out regions of constant bead count.
\subref{beading_transitioning_filtering__transition_ends} We then calculate the end locations (magenta, pink) of the transitions and modify the bead count at nodes in between to fractional values.
\subref{beading_transitioning_filtering__transitions_applied} Finally we introduce nodes at the ends and introduce radial edges (purple) as per the trapezoidation constraint.
The symmetry in the result shows that transitioning is robust against small perturbations in the outline shape.
}
\label{beading_transitioning_filtering}
\end{figure*}

@@

A transition with length $t(n)$ will be placed somewhere covering the transition anchor position.
We require an additional function to be specified by the beading strategy: $t_0(n)$ determines the distance between the lower end of a transition from bead count $n$ to $n+1$ and the anchor point - as measured along the marked bones of the ST.
From that we calculate $t_1(n) = t(n) - t_0(n)$ for the distance from the anchor to the upper end of the transition.
For our example we can simply use $t_0(n) = t_1(n) = \nicefrac12 w_\text{pref}$, so that the transition ramp is centered on the anchor position.

@@

\subsubsection{Beading interpolation}\label{section_beading_interpolation}
Central nodes which are in the middle of a transition have obtained a fractional bead count, but the definition of a beading presupposed integer numbers.
In order to generate a beading for a central node with a fractional bead count assigned we use the fractional part of the bead count to interpolate between two beadings defined on the fractional bead count rounded up and down.
Suppose we want to interpolate between two beadings $B^V$ and $B^W$, for which $n^{B^V} < n^{B^W}$.
We interpolate the diameter $d$, widths $w_i$ and locations $l_i$ for indices $i < \nicefrac12 n^{B^V}$ linearly and enforce the symmetry constraints on the upper indices.
See \cref{beading_interpolation}.
The linear interpolation enforces robustness against small perturbations in the outline shape which cause extra bones to appear in the ST inside of transition regions.

### 2019-08-23 5_generalization.tex
'skeleton'/'graph' => 'ST'

\begin{figure}
\centering
\includegraphics[width=.4\columnwidth]{sources/method/transition_length_limit.pdf}
\caption{
Placement of transition ends (magenta and pink) with respect to the anchor positions of the transitions (purple) on a skeleton segment (blue) with bisector angle $\alpha \approx \SI{135}{\degree}$.
The distance between the anchor position and the upper end ($t_1$) and the distance between the anchor position and the lower end of the transition ($t_0$) should add up to less than the total distance between the anchor positions, which is limited by $\alpha_\text{max}$.
}
\label{transition_placement}
\end{figure}

@@

\paragraph{Constant bead count}
We can emulate the method by \citeauthor{Ding2016a}, by dividing the feature diameter over the widths of a constant number of beads.
Additionally in order to emulate their definition of branches we mark all segments and in a separate algorithm we unmark the outer bones connected to the outline shape.
Note that this deviation from the proposed framework violates the robustness against small perturbations in the outline polygon, since the topology of the skeletal graph is not stable against those.

>>>>

\begin{figure}
\centering
\includegraphics[width=.4\columnwidth]{sources/method/transition_length_limit.pdf}
\caption{
Placement of transition ends (magenta and pink) with respect to the anchor positions of the transitions (purple) on a ST edge (blue) with bisector angle $\alpha \approx \SI{135}{\degree}$.
The distance between the anchor position and the upper end ($t_1$) and the distance between the anchor position and the lower end of the transition ($t_0$) should add up to less than the total distance between the anchor positions, which is limited by $\alpha_\text{max}$.
}
\label{transition_placement}
\end{figure}

@@

\paragraph{Constant bead count}
We can emulate the method by \citeauthor{Ding2016a}, by dividing the feature diameter over the widths of a constant number of beads.
Additionally in order to emulate their definition of branches we mark all segments and in a separate algorithm we unmark the outer bones connected to the outline shape.
Note that this deviation from the proposed framework violates the robustness against small perturbations in the outline polygon, since the topology of the graph of the ST is not stable against those.

### 2019-08-23 6_validation.tex
lil rewording
'skeleton'/'graph' => 'ST'

The algorithmic complexity is limited by the generation of the Voronoi Diagram, which is $O(n \log n)$, where $n$ is the number of vertices in the input shape.
The number of elements in the trapezoidation is linear in the number of elements in the VD
and all of the stages of our framework are also linear in the number of elements in the skeleton,
so the total running time of our algorithm is $O(n \log n)$.

@@

\begin{figure*}
\centering
\setlength{\figwidth}{0.19\textwidth}
\setlength{\figheight}{0.283\textwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_naive_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_naive_widths.png}
\caption{Naive}\label{TEST_naive_accuracy}
\end{subfigure}
%\begin{subfigure}{\figwidth}\centering
%\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_SingleBead_accuracy.png}
%\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_SingleBead_widths.png}
%\caption{Single}\label{TEST_SingleBead_accuracy}
%\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Constant_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Constant_widths.png}
\caption{Constant}\label{TEST_Constant_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Center_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Center_widths.png}
\caption{Center}\label{TEST_Center_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Distributed_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Distributed_widths.png}
\caption{Distributed}\label{TEST_Distributed_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\columnwidth]{sources/validation/gMAT_example/TEST_InwardDistributed_accuracy.png}
\includegraphics[width=\columnwidth]{sources/validation/gMAT_example/TEST_InwardDistributed_widths.png}
\caption{Inward}\label{TEST_InwardDistributed_accuracy}
\end{subfigure}
\begin{subfigure}{.04\columnwidth}\centering
\vspace{4cm}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/widths_legend.png}
\end{subfigure}
\caption{
Visualizing the overfills and underfills and the widths for various beading strategies.
Extrusion beads in gray tones,
blue areas in the top images signify underfill regions,
red areas overfill,
orange areas triply extruded areas (double overfill).
The bottom visualizes the bead widths at each location at \SI{90}{\percent} width.
Cold colors are narrower than the nozzle size $w_\text{pref}$ and warm colors are wider than the nozzle size.
}
\label{visualized_accuracy}
\end{figure*}

@@

\begin{figure}
\centering
\begin{subfigure}{\columnwidth}\centering
\setlength{\figwidth}{\columnwidth}
\includegraphics[width=\figwidth]{sources/applications/P3_print_wedge_naive_edited.png}
\includegraphics[width=\figwidth]{sources/applications/P3_print_wedge_center_edited.png}
\includegraphics[width=\figwidth]{sources/applications/P3_print_wedge_inward_edited.png}
\caption{Wedge}\label{print_wedge}
\end{subfigure}
\caption{
A wedge shape printed using the naive strategy, center deivation strategy and the inward distributed strategy.
The wedge print can be read like a graph with model diameter on the X-axis and the resulting beads over the Y-axis.
The naive and center deviation strategy show problems around certain model diameters.
}
\label{wedge_print}
\end{figure}

>>>>

The algorithmic complexity is limited by the generation of the Voronoi Diagram, which is $O(n \log n)$, where $n$ is the number of vertices in the input shape.
The number of elements in the ST is linear in the number of elements in the VD
and all of the stages of our framework are also linear in the number of elements in the ST,
so the total running time of our algorithm is $O(n \log n)$.

@@

\begin{figure*}
\centering
\setlength{\figwidth}{0.19\textwidth}
\setlength{\figheight}{0.283\textwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_naive_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_naive_widths.png}
\caption{Naive}\label{TEST_naive_accuracy}
\end{subfigure}
%\begin{subfigure}{\figwidth}\centering
%\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_SingleBead_accuracy.png}
%\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_SingleBead_widths.png}
%\caption{Single}\label{TEST_SingleBead_accuracy}
%\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Constant_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Constant_widths.png}
\caption{Constant}\label{TEST_Constant_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Center_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Center_widths.png}
\caption{Center}\label{TEST_Center_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Distributed_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Distributed_widths.png}
\caption{Distributed}\label{TEST_Distributed_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\columnwidth]{sources/validation/gMAT_example/TEST_InwardDistributed_accuracy.png}
\includegraphics[width=\columnwidth]{sources/validation/gMAT_example/TEST_InwardDistributed_widths.png}
\caption{Inward}\label{TEST_InwardDistributed_accuracy}
\end{subfigure}
\begin{subfigure}{.04\columnwidth}\centering
\vspace{4.7cm}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/widths_legend.png}
\end{subfigure}
\caption{
Visualizing the overfills and underfills and the widths for various beading strategies.
Extrusion beads in gray tones,
blue areas in the top images signify underfill regions,
red areas overfill,
orange areas triply extruded areas (double overfill).
The bottom visualizes the bead widths at each location at \SI{90}{\percent} width.
Cold colors are narrower than the nozzle size $w_\text{pref}$ and warm colors are wider than the nozzle size.
}
\label{visualized_accuracy}
\end{figure*}

@@

\begin{figure}
\centering
\begin{subfigure}{\columnwidth}\centering
\setlength{\figwidth}{\columnwidth}
\includegraphics[width=\figwidth]{sources/applications/P3_print_wedge_naive_edited.png}
\includegraphics[width=\figwidth]{sources/applications/P3_print_wedge_center_edited.png}
\includegraphics[width=\figwidth]{sources/applications/P3_print_wedge_inward_edited.png}
\caption{Wedge}\label{print_wedge}
\end{subfigure}
\caption{
A wedge shape printed using the naive strategy, center deivation strategy and the inward distributed strategy.
The naive and center deviation strategy show problems around certain model diameters.
}
\label{wedge_print}
\end{figure}

### 2019-08-23 8_discussion.tex
'skeleton'/'graph' => 'ST'

Note also that our method is robust against small perturbations in the input shape.
Geometrically small changes to the outline shape introduce extra bones and therefore change the topology of the ST graph.
However, the significance measure and beading are defined in terms of radial distances so the robustness of the distance field against such perturbations means our method bypasses the unstability of the skeleton.
Moreover, we have developed a method for dealing with bones within transition regions such that the toolpath is the same as if there wasn't any bone in that region.
The toolpaths generated using our framework therefore remain the same when extra bones are added to the ST.

@@

The constant bead count beading strategy effectively deals with all overfills and underfills, but at the cost of wildly differing bead widths.
See \cref{TEST_Constant_accuracy}.
Note that around regions where the bead width changes a lot we can see some overfill areas, which explains the unusually high overfill statistic in \cref{over_underfill}.
Because the bead count 
For an input outline shape which contains both very small and very large features the algorithm produces bead widths which can fall outside of the range of manufacturable bead widths.
Moreover the skeleton marking is not robust against small perturbations in the outline; adding a small chamfer in a corner causes the unmarked skeleton to be very small at that location, which results in tiny bead widths.

>>>>

Note also that our method is robust against small perturbations in the input shape.
Geometrically small changes to the outline shape introduce extra bones and therefore change the topology of the graph of the ST.
However, the significance measure and beading are defined in terms of radial distances so the robustness of the distance field against such perturbations means our method bypasses the instability of the skeleton.
Moreover, we have developed a method for dealing with bones within transition regions such that the toolpath is the same as if there wasn't any bone in that region.
The toolpaths generated using our framework therefore remain the same when extra bones are added to the ST.

@@

The constant bead count beading strategy effectively deals with all overfills and underfills, but at the cost of wildly differing bead widths.
See \cref{TEST_Constant_accuracy}.
Note that around regions where the bead width changes a lot we can see some overfill areas, which explains the unusually high overfill statistic in \cref{over_underfill}.
Because the bead count 
For an input outline shape which contains both very small and very large features the algorithm produces bead widths which can fall outside of the range of manufacturable bead widths.
Moreover the centrality marking is not robust against small perturbations in the outline; adding a small chamfer in a corner causes the unmarked ST to be very small at that location, which results in tiny bead widths.
